The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2014-09-10 paper/mri paper.tex
ansatz
more paper

\begin{abstract}
The MRI saturates.
\end{abstract}

@@

@@

\beq
\mathcal{L}\mathbf{V_1} = 0
\eeq

@@

\beq
\mathcal{L}\mathbf{V_2} \, = \, \mathbf{N_2} \, - \, \widetilde{\mathcal{L}}_1 \partial_Z \mathbf{V_1}
\eeq

@@

\begin{multline}
\mathcal{D}\partial_T \mathbf{V_1} \, + \, \mathbf{N_3} \, = \, \mathcal{L} \mathbf{V_3} \, + \, \widetilde{\mathcal{L}}_1\partial_Z\mathbf{V_2} \, + \, \widetilde{\mathcal{L}}_2\partial_Z^2\mathbf{V_1} \, \\
- \partial_Z\mathcal{X}\mathbf{V_1} \, - \partial_z^3\mathcal{L}_3\mathbf{V_1}
\end{multline}

The $\mathcal{O}(\epsilon)$ equation is the equation for the linear MRI at marginality.

>>>>

\begin{abstract}
The magnetorotational instability (MRI) is a fundamental process of accretion disk physics, but its saturation mechanism remains poorly understood. We present an analytic analysis of the nonideal MRI in the weakly nonlinear regime -- that is, when the MRI system is just unstable to its most unstable mode. 
\end{abstract}

@@

The multiple scale dependencies of our solution are encoded into an ansatz for the linear MRI solution at marginality,

\beq
\label{V1_ansatz}
\mathbf{V_1} = \alpha(T, Z) \mathbb{V}_{11}(x) e^{i k_c z} + c.c.,
\eeq

where $\alpha$ is a slowly-varying amplitude equation. The $x$ dependence is contained in $\mathbb{V}_{11}$, and must be solved for subject to the radial boundary conditions. The periodic vertical boundary conditions allow us to posit the $z$ dependence, where $k_c$ is the value of the vertical wavenumber at marginality.

@@

\beq
\label{ordere}
\mathcal{L}\mathbf{V_1} = 0
\eeq

@@

\beq
\label{ordere2}
\mathcal{L}\mathbf{V_2} \, = \, \mathbf{N_2} \, - \, \widetilde{\mathcal{L}}_1 \partial_Z \mathbf{V_1}
\eeq

@@

\begin{multline}
\label{ordere3}
\mathcal{D}\partial_T \mathbf{V_1} \, + \, \mathbf{N_3} \, = \, \mathcal{L} \mathbf{V_3} \, + \, \widetilde{\mathcal{L}}_1\partial_Z\mathbf{V_2} \, + \, \widetilde{\mathcal{L}}_2\partial_Z^2\mathbf{V_1} \, \\
- \partial_Z\mathcal{X}\mathbf{V_1} \, - \partial_z^3\mathcal{L}_3\mathbf{V_1}
\end{multline}

The $\mathcal{O}(\epsilon)$ equation is the equation for the linear MRI at marginality. This is the equation that is solved to find the $\mathbb{V}_{11}$ component of Equation \ref{V1_ansatz}.

The partial differential equations that comprise Equations \ref{ordere} to \ref{ordere3} are solved in succession subject to no-slip, perfectly conducting radial boundary conditions, defined as:

\section{Results}
